Pre-/Post-Trikafta (Prospective)

### 2022-04-04 Christine Chan/Pre-post Trikafta Prospective/pre_post_trikafta_prospective_analysis.Rmd
less confusing Ns for chan pre-/post-Trikafta

```{r cgm data,include=FALSE}
# Merge
cgm = read.csv("./Christine Chan/Pre-post Trikafta Prospective/Data_Cleaned/cgm_vars.csv")
cgm$Study.ID = str_extract(cgm$subject_id,"^[[:upper:]]{2}\\d{4}")
cgm$Event.Name = 
  str_extract(tolower(cgm$subject_id),"visit\\d{1}|visit \\d{1}|yr\\d{1}|year\\d{1}|year \\d{1}")
cgm$Event.Name = paste("Visit",gsub("[[:alpha:]]|\\s","",cgm$Event.Name))
df = left_join(df,cgm,by = c("Study.ID", "Event.Name"))
# Update DXA variables
dxa_vars = c("Tissue..g.","Total.Fat.Mass....","Fat.Body.Mass..g.","Fat.Free.Mass..g.",
            "Lean.Body.Mass..g.","Total.Mass..kg.","Fat.Free.Mass..",
            "Fat.Mass.Index..FMI...","Lean.body.mass.fat.mass..LBM.FM.",
            "Fat.Free.Mass.Index...FFMI.","Lean.Body.Mass.Index..LBMI.",
            "BMD.Total.z.score","BMD.Subtotal.z.score",
            "DXA.FMI.calculated.z.score","DXA.LBMI.calculated.z.score")
dxa = read.csv("./Christine Chan/Pre-post Trikafta Prospective/Data_Cleaned/dxa_data.csv")
dxa = dxa %>% select(Study.ID,all_of(dxa_vars))
df = left_join(df,dxa)
keep = dxa$Study.ID
```

@@

```{r results='asis'}
t1 = tableby(~Age.at.visit.+Weight..kg.+weightz+trikafta_duration+
               Sex..Male.1.+BMIz+FEV1..+FVC....+trikafta_duration+
               Genotype+Pancreatic.Status+Kalydeco+Orkambi+Symdeko,
             control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),
             data = df[df$Event.Name == "Visit 1",])
summary(t1,digits = 2,labelTranslations = newlabels)
```

@@

```{r results='asis'}
t1 = tableby(~Age.at.visit.+Weight..kg.+weightz+trikafta_duration+
               Sex..Male.1.+BMIz+FEV1..+FVC....+trikafta_duration+
               Genotype+Pancreatic.Status+Kalydeco+Orkambi+Symdeko,
             control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),
             data = df[df$Event.Name == "Visit 1" & df$Study.ID %in% keep,])
summary(t1,digits = 2,labelTranslations = newlabels)
```

@@

```{r results='asis'}
t2_vars = c("A1C.result","Weight..kg.","BMIz","FEV1..","FVC....","trikafta_duration",
            "Group","Glucose.0.minute",
            "Glucose.60.min","Glucose.120.min","c.peptide.0.minute",
            "`Glucose iAUC`","`C Peptide iAUC`","`Insulin iAUC`",
            "`C Peptide Index`","Matsuda",
            "`Adapted Matsuda`","`C Peptide ODI`","`ODI (Cpeptide index x Matsuda)`",
            "iAUC_ratio","homa2B","homa2S","homa2IR",
            "Tissue..g.","Total.Fat.Mass....","Fat.Body.Mass..g.","Fat.Free.Mass..g.",
            "Lean.Body.Mass..g.","Total.Mass..kg.","Fat.Free.Mass..",
            "Fat.Mass.Index..FMI...","Lean.body.mass.fat.mass..LBM.FM.",
            "Fat.Free.Mass.Index...FFMI.","Lean.Body.Mass.Index..LBMI.",
            "BMD.Total.z.score","BMD.Subtotal.z.score",
            "DXA.FMI.calculated.z.score","DXA.LBMI.calculated.z.score",
            "mean_sensor","max_sensor","min_sensor","percent_time_70_180",
            "percent_time_over_140","percent_time_over_180","percent_time_over_250",
            "percent_time_under_70","percent_time_under_54","standard_deviation","cv","r_mage")
f = as.formula(paste0("Event.Name ~ ",paste0(t2_vars,collapse = "+")))
p <- paired(f,data = df, id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F,
            control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),)
summary(p,pfootnote = T,labelTranslations = newlabels)
```

@@

```{r results='asis'}
f = as.formula(paste0("Event.Name ~ ",paste0(t2_vars,collapse = "+")))
p = paired(f,data = df[!is.na(df$date_cgm_placement) & df$Study.ID %in% keep,], 
           control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),
           id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F)
summary(p,pfootnote = T,labelTranslations = newlabels)
```

@@

```{r results='asis'}
f = as.formula(paste0("Event.Name ~ ",paste0(t2_vars,collapse = "+")))
p <- paired(f,data = df, id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F,
            control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),
            strata = `Age Group`)
summary(p,pfootnote = T,labelTranslations = newlabels)
```

>>>>

```{r cgm data,include=FALSE}
# Merge
cgm = read.csv("./Christine Chan/Pre-post Trikafta Prospective/Data_Cleaned/cgm_vars.csv")
cgm$Study.ID = str_extract(cgm$subject_id,"^[[:upper:]]{2}\\d{4}")
cgm$Event.Name = 
  str_extract(tolower(cgm$subject_id),"visit\\d{1}|visit \\d{1}|yr\\d{1}|year\\d{1}|year \\d{1}")
cgm$Event.Name = paste("Visit",gsub("[[:alpha:]]|\\s","",cgm$Event.Name))
df = left_join(df,cgm,by = c("Study.ID", "Event.Name"))
keep_a1c = df %>% group_by(Study.ID) %>% 
  summarise(n = sum(!is.na(A1C.result))) %>%
  filter(n == 2) %>% pull(Study.ID)
# Update DXA variables
dxa_vars = c("Tissue..g.","Total.Fat.Mass....","Fat.Body.Mass..g.","Fat.Free.Mass..g.",
            "Lean.Body.Mass..g.","Total.Mass..kg.","Fat.Free.Mass..",
            "Fat.Mass.Index..FMI...","Lean.body.mass.fat.mass..LBM.FM.",
            "Fat.Free.Mass.Index...FFMI.","Lean.Body.Mass.Index..LBMI.",
            "BMD.Total.z.score","BMD.Subtotal.z.score",
            "DXA.FMI.calculated.z.score","DXA.LBMI.calculated.z.score")
dxa = read.csv("./Christine Chan/Pre-post Trikafta Prospective/Data_Cleaned/dxa_data.csv")
dxa = dxa %>% select(Study.ID,all_of(dxa_vars))
df = left_join(df,dxa)
keep_dxa = dxa$Study.ID
```

@@

```{r results='asis'}
t1 = tableby(~Age.at.visit.+Weight..kg.+weightz+trikafta_duration+
               Sex..Male.1.+BMIz+FEV1..+FVC....+trikafta_duration+
               Genotype+Pancreatic.Status+Kalydeco+Orkambi+Symdeko,
             control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),
             data = df[df$Event.Name == "Visit 1" & df$Study.ID %in% keep_a1c,])
summary(t1,digits = 2,labelTranslations = newlabels)
```

@@

```{r results='asis'}
t1 = tableby(~Age.at.visit.+Weight..kg.+weightz+trikafta_duration+
               Sex..Male.1.+BMIz+FEV1..+FVC....+trikafta_duration+
               Genotype+Pancreatic.Status+Kalydeco+Orkambi+Symdeko,
             control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),
             data = df[df$Event.Name == "Visit 1" & df$Study.ID %in% keep_dxa,])
summary(t1,digits = 2,labelTranslations = newlabels)
```

@@

```{r results='asis'}
t2_vars = c("A1C.result","Weight..kg.","BMIz","FEV1..","FVC....","trikafta_duration",
            "Group","Glucose.0.minute",
            "Glucose.60.min","Glucose.120.min","c.peptide.0.minute",
            "`Glucose iAUC`","`C Peptide iAUC`","`Insulin iAUC`",
            "`C Peptide Index`","Matsuda",
            "`Adapted Matsuda`","`C Peptide ODI`","`ODI (Cpeptide index x Matsuda)`",
            "iAUC_ratio","homa2B","homa2S","homa2IR",
            "Tissue..g.","Total.Fat.Mass....","Fat.Body.Mass..g.","Fat.Free.Mass..g.",
            "Lean.Body.Mass..g.","Total.Mass..kg.","Fat.Free.Mass..",
            "Fat.Mass.Index..FMI...","Lean.body.mass.fat.mass..LBM.FM.",
            "Fat.Free.Mass.Index...FFMI.","Lean.Body.Mass.Index..LBMI.",
            "BMD.Total.z.score","BMD.Subtotal.z.score",
            "DXA.FMI.calculated.z.score","DXA.LBMI.calculated.z.score",
            "mean_sensor","max_sensor","min_sensor","percent_time_70_180",
            "percent_time_over_140","percent_time_over_180","percent_time_over_250",
            "percent_time_under_70","percent_time_under_54","standard_deviation","cv","r_mage")
f = as.formula(paste0("Event.Name ~ ",paste0(t2_vars,collapse = "+")))
p <- paired(f,data = df[df$Study.ID %in% keep_a1c,], id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F,
            control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),)
summary(p,pfootnote = T,labelTranslations = newlabels)
```

@@

```{r results='asis'}
f = as.formula(paste0("Event.Name ~ ",paste0(t2_vars,collapse = "+")))
p = paired(f,data = df[df$Study.ID %in% keep_dxa,], 
           control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),
           id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F)
summary(p,pfootnote = T,labelTranslations = newlabels)
```

@@

```{r results='asis'}
f = as.formula(paste0("Event.Name ~ ",paste0(t2_vars,collapse = "+")))
p <- paired(f,data = df[df$Study.ID %in% keep_a1c,], id = Study.ID,numeric.test = "signed.rank",signed.rank.exact = F,
            control = tableby.control(numeric.stats = c(c("Nmiss", "medianq1q3", "range"))),
            strata = `Age Group`)
summary(p,pfootnote = T,labelTranslations = newlabels)
```
